A Vignetted View of Computer Science through Citation Analysis

### 2019-12-20 Scientometrics/comp.tex
update

\begin{table}[ht]
\caption{\emph{denominator is 2090947 (some source ids got lost via inner joins and code restrictions) Statistics regarding the 20 clusters produced using direct citation. The \emph{comp} dataset 
2685021 is because of inner joins on ASJC Explain conductance calculations~\cite{shun_parallel_2016}}}
\label{tab:comp}       
\begin{tabular}{lrccc}
\hline\noalign{\smallskip}
minor\_subject\_area & Percent of Publications \\
\noalign{\smallskip}\hline\noalign{\smallskip}
Software & 30.1 \\
Computer Science Applications & 25.0 \\ 
Computer Networks and Communications & 21.5 \\
Theoretical Computer Science & 19.6 \\ 
Computer Science(all) & 19.4 \\ 
Artificial Intelligence & 14.2 \\ 
Information Systems & 11.8 \\ 
Hardware and Architecture & 11.8 \\ 
Signal Processing & 9.8 \\ 
Computer Vision and Pattern Recognition & 9.4 \\ 
Computational Theory and Mathematics & 7.9 \\ 
Human-Computer Interaction & 7.4 \\ 
Computer Graphics and Computer-Aided Design & 5.2 \\ 
Computer Science (miscellaneous) & 0.9 \\ 
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
\newpage

\begin{table}[ht]
\caption{\emph{Statistics regarding the 20 clusters produced using direct citation. The \emph{comp} dataset 
2685021 is because of inner joins on ASJC Explain conductance calculations~\cite{shun_parallel_2016}}}
\label{tab:graclus}       
\begin{tabular}{lrccc}
\hline\noalign{\smallskip}
Cluster & Publications & Conductance & Total ASJC Labels & Unique ASJC Labels\\
\noalign{\smallskip}\hline\noalign{\smallskip}
0 & 111,294 & 0.12 & 265,664 & 142 \\ 
1 & 117,057 & 0.14 & 246,960 & 166 \\ 
2 & 116,251 & 0.11 & 280,602 & 165 \\ 
3 & 353,366 & 0.15 & 881,693 & 200 \\ 
4 & 145,081 & 0.09 & 349,020 & 154 \\ 
5 & 92,097 & 0.17 & 248,168 & 186 \\ 
6 & 71,865 & 0.15 & 199,681 & 163 \\ 
7 & 179,927 & 0.18 & 465,181 & 202 \\ 
8 & 302,656 & 0.18 & 760,117 & 214 \\ 
9 & 69,520 & 0.19 & 197,031 & 174 \\ 
10 & 42,462 & 0.10 & 102,838 & 141 \\ 
11 & 448,030 & 0.25 & 1,229,061 & 224 \\ 
12 & 70,738 & 0.21 & 216,546 & 179 \\ 
13 & 105,232 & 0.17 & 289,318 & 187 \\ 
14 & 199,176 & 0.15 & 551,657 & 208 \\ 
15 & 64,384 & 0.17 & 195,679 & 167 \\ 
16 & 89,340 & 0.11 & 240,157 & 158 \\ 
17 & 50,817 & 0.14 & 181,531 & 179 \\ 
18 & 43,113 & 0.20 & 108,518 & 177 \\ 
19 & 12,615 & 0.80 & 36,583 & 229 \\ 
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
\newpage

\begin{table}[ht]
\caption{\emph{Co-citation Centroid}}
\label{tab:centroid_reconcile}       
\begin{tabular}{p{8 mm}p{42 mm}l}
\hline\noalign{\smallskip}
Cluster & Label & CC  \\
\noalign{\smallskip}\hline
18670 & Dynamical Systems & EEE (14)  \newline Control/Systems Eng (14) \\
18892 & Operations Research & EEE (24) \\ 
18918 & Image Processing & EEE (17)  \newline Software (17) \\ 
18947 & Robotics & Software (12) \\ 
18956 & Computer Vision & Comp Graphics and Comp-Aided Design (21)\\ 
18972 & Software & Software (55) \\ 
18974 & Applied Mathematics & Applied Mathematics (12)\\ 
18983 & Optimization & EEE (35) \\ 
18997 & Chaotic Systems & Control/Systems Eng (23)\\ 
19008 & Hum Comp Interaction & Education (19)\\ 
19009 & Artificial Intelligence & Computer Vision and Pattern Recognition (32)\\ 
19013 & Security & Computer Science(all) (29)\\ 
19026 & Architecture & EEE (35) \\ 
19027 & Graph algorithms & Computer Networks and Communications (19)\\ 
19030 & Databases & Software (19)\\ 
19031 & Networks & EEE (32)\\ 
19033 & Facial Recognition & Comp Vision and Pattern Recognition (18)\\ 
19034 & Neurology & Neurology (12)\\ 
19035 & Intelligent Systems & Artificial Intelligence (17)\\ 
19036 & Comp Geometry & Software (10)\\ 
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{\emph{Co-citation Centroid}}
\label{tab:centroid}       
\begin{tabular}{p{8 mm}p{42 mm}ll}
\hline\noalign{\smallskip}
Cluster & Nucleating Pair & NCF & Label \\
\noalign{\smallskip}\hline
18670 & 10.1016/j.cam.2015.03.057 10.1016/j.sigpro.2015.10.009 & 0.92 & Dynamical Systems \\
18892 & 10.1287/msom.1080.0228 10.1287/msom.1060.0190 & 0.72 & Operations Research\\ 
18918 & 10.1007/s11128-010-0177-y 10.1007/s11128-013-0567-z & 0.83 & Image Processing\\ 
18947 & 10.1109/TASE.2011.2160452 10.1109/TASE.2011.2178023 & 0.77 & Robotics\\ 
18956 & 10.1109/ICCV.2017.32 10.1109/ICCV.2017.31 & 0.84 & Computer Vision\\ 
18972 & 10.1109/ASE.2013.6693094 10.1145/2568225.2568254 & 0.69 & Software \\ 
18974 & 10.1016/j.amc.2009.03.023 10.1016/j.amc.2010.07.064 & 0.54 & Applied Mathematics\\ 
18983 & 10.1137/110848864 10.1137/110848876 & 0.66 & Optimization\\ 
18997 & 10.1504/IJMIC.2014.065339 10.1504/IJMIC.2015.068871 & 0.91 & Chaotic Systems \\ 
19008 & 10.1016/j.chb.2008.12.013 10.1016/j.chb.2008.12.012 & 0.63 & Hum Comp Interaction\\ 
19009 & 10.1109/AVSS.2017.8078491 10.1109/ICCV.2017.206 & 0.78 & Artificial Intelligence\\ 
19013 & 10.1145/2508859.2516668 10.1007/978-3-642-42045-0\_15 & 0.88 & Security\\ 
19026 & 10.1145/2541940.2541942 10.1109/HPCA.2014.6835965 & 0.81 & Architecture\\ 
19027 & 10.1016/S0305-0548(03)00250-8 10.1016/j.ejor.2006.03.013 & 0.82 & Graph algorithms\\ 
19030 & 10.1109/ICDE.2008.4497474 10.14778/1687627.1687666 & 0.69 & Databases \\ 
19031 & 10.1109/TMM.2005.843347 10.1109/TCE.2005.1405724 & 0.55 & Networks\\ 
19033 & 10.1109/TIFS.2014.2327757 10.1109/TCYB.2014.2376934 & 0.78 & Facial Recognition\\ 
19034 & 10.1016/j.neuroimage.2013.05.018 10.1016/j.neuroimage.2014.06.016 & 0.63 & Neurology\\ 
19035 & 10.1002/int.21933 10.1002/int.21927 & 1.09 & Intelligent Systems\\ 
19036 & 10.1006/jsco.2000.0402 10.1006/jsco.2000.0403 & 0.73 & Comp Geometry\\ 
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
\newpage

>>>>

\begin{table}[ht]
\caption{Characterization of the \emph{comp} dataset relative to Scopus ASJC minor subject areas.}
\label{tab:comp}       
\begin{tabular}{lrccc}
\hline\noalign{\smallskip}
minor\_subject\_area & Percent of Publications \\
\noalign{\smallskip}\hline\noalign{\smallskip}
Software & 30.1 \\
Computer Science Applications & 25.0 \\ 
Computer Networks and Communications & 21.5 \\
Theoretical Computer Science & 19.6 \\ 
Computer Science(all) & 19.4 \\ 
Artificial Intelligence & 14.2 \\ 
Information Systems & 11.8 \\ 
Hardware and Architecture & 11.8 \\ 
Signal Processing & 9.8 \\ 
Computer Vision and Pattern Recognition & 9.4 \\ 
Computational Theory and Mathematics & 7.9 \\ 
Human-Computer Interaction & 7.4 \\ 
Computer Graphics and Computer-Aided Design & 5.2 \\ 
Computer Science (miscellaneous) & 0.9 \\ 
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
\newpage

\begin{table}[ht]
\caption{Descriptive statistics of the 20 clusters produced from the \emph{dataset} using Graclus (direct citation).  The number of publications in each cluster, the conductance~\cite{shun_parallel_2016} of each cluster, the total number ASJC minor subject area labels assigned to publications in each cluster and the number of 
unique labels in each cluster are shown}
\label{tab:graclus}       
\begin{tabular}{lrccc}
\hline\noalign{\smallskip}
Cluster & Publications & Conductance & Total ASJC Labels & Unique ASJC Labels\\
\noalign{\smallskip}\hline\noalign{\smallskip}
0 & 111,294 & 0.12 & 265,664 & 142 \\ 
1 & 117,057 & 0.14 & 246,960 & 166 \\ 
2 & 116,251 & 0.11 & 280,602 & 165 \\ 
3 & 353,366 & 0.15 & 881,693 & 200 \\ 
4 & 145,081 & 0.09 & 349,020 & 154 \\ 
5 & 92,097 & 0.17 & 248,168 & 186 \\ 
6 & 71,865 & 0.15 & 199,681 & 163 \\ 
7 & 179,927 & 0.18 & 465,181 & 202 \\ 
8 & 302,656 & 0.18 & 760,117 & 214 \\ 
9 & 69,520 & 0.19 & 197,031 & 174 \\ 
10 & 42,462 & 0.10 & 102,838 & 141 \\ 
11 & 448,030 & 0.25 & 1,229,061 & 224 \\ 
12 & 70,738 & 0.21 & 216,546 & 179 \\ 
13 & 105,232 & 0.17 & 289,318 & 187 \\ 
14 & 199,176 & 0.15 & 551,657 & 208 \\ 
15 & 64,384 & 0.17 & 195,679 & 167 \\ 
16 & 89,340 & 0.11 & 240,157 & 158 \\ 
17 & 50,817 & 0.14 & 181,531 & 179 \\ 
18 & 43,113 & 0.20 & 108,518 & 177 \\ 
19 & 12,615 & 0.80 & 36,583 & 229 \\ 
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
\newpage

\begin{table}[ht]
\caption{\emph{Nucleating Co-citations.} For each of the 20 co-citation clusters, the pair with the strongest edge (greatest normalized co-citation frequency) is shown below along with a manually assigned label}
\label{tab:centroid}       
\begin{tabular}{p{8 mm}p{42 mm}ll}
\hline\noalign{\smallskip}
Cluster & Nucleating Pair & NCF & Manual Label \\
\noalign{\smallskip}\hline
18670 & 10.1016/j.cam.2015.03.057 10.1016/j.sigpro.2015.10.009 & 0.92 & Dynamical Systems \\
18892 & 10.1287/msom.1080.0228 10.1287/msom.1060.0190 & 0.72 & Operations Research\\ 
18918 & 10.1007/s11128-010-0177-y 10.1007/s11128-013-0567-z & 0.83 & Image Processing\\ 
18947 & 10.1109/TASE.2011.2160452 10.1109/TASE.2011.2178023 & 0.77 & Robotics\\ 
18956 & 10.1109/ICCV.2017.32 10.1109/ICCV.2017.31 & 0.84 & Computer Vision\\ 
18972 & 10.1109/ASE.2013.6693094 10.1145/2568225.2568254 & 0.69 & Software \\ 
18974 & 10.1016/j.amc.2009.03.023 10.1016/j.amc.2010.07.064 & 0.54 & Applied Mathematics\\ 
18983 & 10.1137/110848864 10.1137/110848876 & 0.66 & Optimization\\ 
18997 & 10.1504/IJMIC.2014.065339 10.1504/IJMIC.2015.068871 & 0.91 & Chaotic Systems \\ 
19008 & 10.1016/j.chb.2008.12.013 10.1016/j.chb.2008.12.012 & 0.63 & Hum Comp Interaction\\ 
19009 & 10.1109/AVSS.2017.8078491 10.1109/ICCV.2017.206 & 0.78 & Artificial Intelligence\\ 
19013 & 10.1145/2508859.2516668 10.1007/978-3-642-42045-0\_15 & 0.88 & Security\\ 
19026 & 10.1145/2541940.2541942 10.1109/HPCA.2014.6835965 & 0.81 & Architecture\\ 
19027 & 10.1016/S0305-0548(03)00250-8 10.1016/j.ejor.2006.03.013 & 0.82 & Graph algorithms\\ 
19030 & 10.1109/ICDE.2008.4497474 10.14778/1687627.1687666 & 0.69 & Databases \\ 
19031 & 10.1109/TMM.2005.843347 10.1109/TCE.2005.1405724 & 0.55 & Networks\\ 
19033 & 10.1109/TIFS.2014.2327757 10.1109/TCYB.2014.2376934 & 0.78 & Facial Recognition\\ 
19034 & 10.1016/j.neuroimage.2013.05.018 10.1016/j.neuroimage.2014.06.016 & 0.63 & Neurology\\ 
19035 & 10.1002/int.21933 10.1002/int.21927 & 1.09 & Intelligent Systems\\ 
19036 & 10.1006/jsco.2000.0402 10.1006/jsco.2000.0403 & 0.73 & Comp Geometry\\ 
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
\newpage

\begin{table}[ht]
\caption{\emph{Nucleating Co-citations} Manually assigned labels for nucleating co-cited pairs (Table~\ref{tab:centroid}) are matched to the ASJC minor subject area that constitutes the largest fraction (shown as percentage in parentheses) of all nodes in the cluster. In cases of ties, both minor subject areas are shown. Abbreviations: Electrical and Electronic Engineering (EEE); Control and Systems Engineering (CSE)}
\label{tab:centroid_reconcile}       
\begin{tabular}{p{8 mm}p{42 mm}l}
\hline\noalign{\smallskip}
Cluster & Label & Minor Subject Area \\
\noalign{\smallskip}\hline
18670 & Dynamical Systems & (i) EEE (14) (ii) CSE (14) \\
18892 & Operations Research & EEE (24) \\ 
18918 & Image Processing & (i) EEE (17) (ii) Software (17) \\ 
18947 & Robotics & Software (12) \\ 
18956 & Computer Vision & Computer Graphics and Computer-Aided Design (21)\\ 
18972 & Software & Software (55) \\ 
18974 & Applied Mathematics & Applied Mathematics (12)\\ 
18983 & Optimization & EEE (35) \\ 
18997 & Chaotic Systems & CSE (23)\\ 
19008 & Hum Comp Interaction & Education (19)\\ 
19009 & Artificial Intelligence & Computer Vision and Pattern Recognition (32)\\ 
19013 & Security & Computer Science(all) (29)\\ 
19026 & Architecture & EEE (35) \\ 
19027 & Graph algorithms & Computer Networks and Communications (19)\\ 
19030 & Databases & Software (19)\\ 
19031 & Networks & EEE (32)\\ 
19033 & Facial Recognition & Computer Vision and Pattern Recognition (18)\\ 
19034 & Neurology & Neurology (12)\\ 
19035 & Intelligent Systems & Artificial Intelligence (17)\\ 
19036 & Comp Geometry & Software (10)\\ 
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
\newpage
